### 2016-02-09 mcmc.tex
priors wrong

% to-do
% -----
% - Kill all issues in this list, below:
% - Deal with all mentions of ``DFM'' or ``HOGG''
% - Go through github issues, if any.
% - Systematically cite chapters of Brooks \etal in each section.
% - mention Gelman--Rubin statistic
% - mention JAGS and STAN in methods section
% - follow up the idea that burn-in doesn't exist at all!  It does for emcee.
% - need to mention case where there is an MC integral INSIDE the likelihood function
% - need to mention testing the likelihood function, by, say, 1-d scans back and forth.
% - would love to have the Note symbols to be links to the notes and the notes to have links back to the main text...!
% - send to friendlies for comments
%   - Gelman
%   - Goodman
%   - Lang
%   - Rix
%   - Bovy
%   - Brewer
% - post on arXiv

@@

If you \emph{do} return posterior samples to your audience, how many
should you return?
There are only heuristic answers to this, but a guideline is that, if
you only care about a single (one-dimensional) parameter, you don't
need many samples; a dozen suffices to give you a reasonable posterior
pdf mean and variance.\note{HOGG cite Mackay.}
If you care about $K$ parameters or dimensions of the parameter space,
in general the need for samples grows exponentially (or perhaps even
factorially!) with the number of dimensions.\note{HOGG cite something.}
So if you have a ten-dimensional space, expect to be publishing your
samples in an electronic table on the web!
If you \emph{do} publish sufficient numbers of posterior samples, you
might find users who want to make serious use of them.\note{HOGG cite
  our importance-sampling papers with some explanation here.}

@@

Another important functional test is to \emph{sample the prior pdf}.
This tests the sampler,
  tests that your priors really are what you think they are
  (and there are so many ways for them \emph{not} to be\note{HOGG}),
  and tests that your prior pdfs are proper
  (functions that can be normalized).
This test is most effective as a true end-to-end test of your model
  if you structure your code such that the log probability function \code{lnprob}
  input to the \MCMC\ scheme
  is set up as a sum of a log likelihood function \code{lnlikelihood}
  and a prior function \code{lnprior}.
The sampler can be switched to sampling the prior by a simple replacement
  of the \code{lnlikelihood} function
  with a trivial function that always returns zero.

@@

>>>>

% to-do
% -----
% - Kill all issues in this list, below
% - Deal with all mentions of ``DFM'' or ``HOGG''
% - Go through github issues, if any.
% - Systematically cite chapters of Brooks \etal in each section.
% - Skim MacKay and make sure we cite him in any relevant place.
% - mention Gelman--Rubin statistic
% - mention JAGS and STAN in methods section
% - follow up the idea that burn-in doesn't exist at all!  It does for emcee.
% - need to mention case where there is an MC integral INSIDE the likelihood function
% - need to mention testing the likelihood function, by, say, 1-d scans back and forth.
% - would love to have the Note symbols to be links to the notes and the notes to have links back to the main text...!
% - send to friendlies for comments
%   - Gelman
%   - Goodman
%   - Lang
%   - Rix
%   - Bovy
%   - Brewer
% - post on arXiv

@@

If you \emph{do} return posterior samples to your audience, how many
should you return?
There are only heuristic answers to this, but a guideline is that, if
you only care about a single (one-dimensional) parameter, you don't
need many samples; a dozen suffices to give you a reasonable posterior
pdf mean and variance.\note{This point is made well by \citet{mackay}.}
If you care about $K$ parameters or dimensions of the parameter space,
in general the need for samples grows exponentially (or perhaps even
factorially!) with the number of dimensions.\note{HOGG cite something.}
So if you have a ten-dimensional space, expect to be publishing your
samples in an electronic table on the web!
If you \emph{do} publish sufficient numbers of posterior samples, you
might find users who want to make serious use of them.\note{HOGG cite
  our importance-sampling papers with some explanation here.}

@@

Another important functional test is to \emph{sample the prior pdf}.
This tests the sampler,
  tests that your priors really are what you think they are
  (and there are so many ways for them \emph{not} to be\note{It is
    easy to think you have flat priors when in practice your sampler
    has flat priors in the logarithms of the parameters or inverses of
    the parameters.  Also, it is easy to have improper priors when you
    think they are proper, because limits are not working, or you were
    wrong about the convergence of some integral.  Sometimes the prior pdf in practice has
    different edges than you think because there is some censoring
    happening that you haven't considered.  And then, of course, it is
    possible for your sampler itself to be buggy.}), and tests that
  your prior pdfs are proper (functions that can be normalized).
This test is most effective as a true end-to-end test of your model
  if you structure your code such that the log probability function \code{lnprob}
  input to the \MCMC\ scheme
  is set up as a sum of a log likelihood function \code{lnlikelihood}
  and a prior function \code{lnprior}.
The sampler can be switched to sampling the prior by a simple replacement
  of the \code{lnlikelihood} function
  with a trivial function that always returns zero.

@@

\bibitem[MacKay(2003)]{mackay}
  MacKay,~D.~J.~C., 2003,
  \href{http://www.inference.phy.cam.ac.uk/mackay/itila/book.html}{\textit{Inference, Information Theory, and Learning Algorithms}},
  Cambridge University Press
  \isbn{9780521642989}.
